### 2022-12-22 sections/experiments/_real_world.qmd
more work on transfer to this repo

```{julia}
max_obs = 2500
data_sets = AlgorithmicRecourseDynamics.Data.load_real_world(max_obs; data_dir=data_path)
choices = [
    :cal_housing, 
    :credit_default, 
    :gmsc, 
]
data_sets = filter(p -> p[1] in choices, data_sets)
```

@@

>>>>

```{julia}
max_obs = 2500
data_sets = load_real_world(max_obs; data_dir=data_path)
choices = [
    :cal_housing, 
    :credit_default, 
    :gmsc, 
]
data_sets = filter(p -> p[1] in choices, data_sets)
```

@@

```{julia}
experiments = set_up_experiments(
    data_sets, models, generators; 
    pre_train_models=100, model_params=model_params, 
    data_loader=data_loader
)
```

### 2022-12-22 sections/experiments/_synthetic.qmd
more work on transfer to this repo

#### Experiments

@@

include("src/setup.jl")
eval(setup)
output_path = output_dir("synthetic") # output directory for artifacts
www_path = www_dir("synthetic")       # output directory for images
```

```{julia}
max_obs = 1000
catalogue = AlgorithmicRecourseDynamics.Data.load_synthetic(max_obs)
choices = [
    :linearly_separable, 
    :overlapping, 
    :circles, 
    :moons,
]
data_sets = filter(p -> p[1] in choices, catalogue)
```

@@

>>>>

#### Experiment

@@

include("src/setup.jl")
eval(setup)
output_path = output_dir("synthetic") # output directory for artifacts
www_path = www_dir("synthetic")       # output directory for images
data_path = data_dir("synthetic")
```

@@

```{julia}
max_obs = 1000
catalogue = AlgorithmicRecourseDynamics.Data.load_synthetic(max_obs; data_dir=data_path)
choices = [
    :linearly_separable, 
    :overlapping, 
    :circles, 
    :moons,
]
data_sets = filter(p -> p[1] in choices, catalogue)
```
